---
title: 'Infliximab: Time-Weighted Bayesian Estimation'
author: "Jessica Wojciechowski"
date: "7 July 2016"
output: 
  html_document: 
    fig_width: 10
    highlight: textmate
---

```{r,echo = TRUE,warning = FALSE}
# Set working directory
  project.dir <- "/Volumes/Prosecutor/PhD/InfliximabBayes/infliximab-bayes/Project/"
  n <- 12  # Number of seed individuals that were simulated
  nsim <- 200 # Number of simulations of seed individuals
  error.model <- "_log-normal-error"  # Residual error model (testing proportional and log-normal)
  sim.output.dir <- paste0("SIM",nsim,"_IND",n,error.model)
  output.dir <- paste0("/Volumes/Prosecutor/PhD/InfliximabBayes/infliximab-output/",sim.output.dir,"/")
  
# Set up folder to save the processed output
  save.dir <- "/Volumes/Prosecutor/PhD/InfliximabBayes/infliximab-bayes-plots/"
  dir.create(file.path(paste0(save.dir,sim.output.dir,"/")),showWarnings = FALSE)
  
# Load package libraries
  library(ggplot2)  # Plotting
  library(grid)  # Plotting
  library(plyr)  # ddply function
  
# Custom ggplot2 theme
	theme_bw2 <- theme_set(theme_bw(base_size = 14))  
  
# Pre-specified functions
  CI95lo <- function(x) quantile(x,probs = 0.025)  # Calculate 2.5th percentile
  CI95hi <- function(x) quantile(x,probs = 0.975)  # Calculate 97.5th percentile
  
  # Summary function for calculating median and prediction intervals
    summary.function <- function(x) {
      median <- median(x)
      stat.95lo <- CI95lo(x)
      stat.95hi <- CI95hi(x)
      result <- c(median,stat.95lo,stat.95hi)
      names(result)[c(1,2,3)] <- c("median","stat.95lo","stat.95hi")
      result
    }
  
# Pre-specified objects
  trough.target <- 3  # Don't want to be below the trough
  trough.upper <- 5  # Don't want concentrations to be too high - waste of drug
  infusion.times <- c(0,14,42,98,154,210,266,322,378,434,490,546)
  scale.log10.labels <- c(0.01,0.1,1,10,100,1000)
  sample.time1 <- 98  # Sampling time at the end of interval 1
  sample.time2 <- 210  # Sampling time at the end of interval 2
  sample.time3 <- 378  # Sampling time at the end of interval 3
  sample.time4 <- 546  # Sampling time at the end of interval 4
  sample.times <- c(sample.time1,sample.time2,sample.time3,sample.time4)
```

## Read in output

Exclude individuals that are in SIM = 0 (these were only added to see what would happen in the population typical for each seed individual).

Add an identifier label for each study.

```{r,echo = TRUE,warning = FALSE}
# Label simulation
  label.data <- read.csv(file = paste0(output.dir,"label_simulation.csv"))
  label.data <- label.data[label.data$SIM != 0,]
  label.data$STUDY <- 1
  # Append an ERRPRO column (because this data frame doesn't have it)
    label.data$ERRPRO <- 0
    label.data <- label.data[,c(1:4,21,5:20)]
    label.data$STUDYf <- "Label"
  
# Clinical simulation
  clinical.data <- read.csv(file = paste0(output.dir,"clinical_simulation.csv"))
  clinical.data <- clinical.data[clinical.data$SIM != 0,]
  clinical.data$STUDY <- 2
  clinical.data$STUDYf <- "Clinical"
  
# Bayesian - No Time-Weighting
  method1 <- "NTimeWeight"
  covariate1 <- "AllCov"
  bayes.data1 <- read.csv(file = paste0(output.dir,method1,covariate1,"/",method1,covariate1,"_optimise_bayes_simulation.csv"))
  bayes.data1 <- bayes.data1[bayes.data1$SIM != 0,]    
  bayes.data1$STUDY <- 3
  bayes.data1$STUDYf <- paste0(method1,covariate1)
  
# Bayesian - Peck 1.005
  method2 <- "Peck1.005"
  bayes.data2 <- read.csv(file = paste0(output.dir,method2,covariate1,"/",method2,covariate1,"_optimise_bayes_simulation.csv"))
  bayes.data2 <- bayes.data2[bayes.data2$SIM != 0,]
  bayes.data2$STUDY <- 4
  bayes.data2$STUDYf <- paste0(method2,covariate1)
  
# Bayesian - Peck 1.01
  method3 <- "Peck1.01"
  bayes.data3 <- read.csv(file = paste0(output.dir,method3,covariate1,"/",method3,covariate1,"_optimise_bayes_simulation.csv"))
  bayes.data3 <- bayes.data3[bayes.data3$SIM != 0,]      
  bayes.data3$STUDY <- 5
  bayes.data3$STUDYf <- paste0(method3,covariate1)
  
# Combine all of the data frames
  all.data <- rbind(label.data,clinical.data,bayes.data1,bayes.data2,bayes.data3)
```

## Plot concentration-time for all studies

Represented as median and 95% prediction intervals

```{r,echo = TRUE,warning = FALSE}
# Line (median) and ribbon (prediction intervals)
  plotobj1 <- NULL
  plotobj1 <- ggplot(all.data)
  plotobj1 <- plotobj1 + stat_summary(aes(x = time,y = IPRE,colour = STUDYf),geom = "line",fun.y = median)
  plotobj1 <- plotobj1 + stat_summary(aes(x = time,y = IPRE,fill = STUDYf),geom = "ribbon",fun.ymin = "CI95lo",fun.ymax = "CI95hi",alpha = 0.3)
  plotobj1 <- plotobj1 + geom_hline(aes(yintercept = trough.target),linetype = "dashed")
  plotobj1 <- plotobj1 + scale_x_continuous("\nTime (days)")
  plotobj1 <- plotobj1 + scale_y_log10("Infliximab Concentration (mg/L)")
  plotobj1 <- plotobj1 + facet_wrap(~STUDYf)
  plotobj1 <- plotobj1 + theme(legend.position = "none")
  print(plotobj1)
```

## Summarise AUT at time = 546 days for all studies

AUT = Time spent under the target trough concentration (3 mg/L)

```{r,echo = TRUE,warning = FALSE}
# Subset data frame for only time == 546
  all.data.546 <- all.data[all.data$time == 546,]
# Calculate median and percentiles for AUT at 546 for all studies
  summary.AUT.546 <- ddply(all.data.546, .(STUDYf), function(all.data.546) summary.function(all.data.546$AUT))
  print(summary.AUT.546)
  
# Plot boxplots
  plotobj2 <- NULL
  plotobj2 <- ggplot(all.data.546)
  plotobj2 <- plotobj2 + geom_boxplot(aes(x = STUDYf,y = AUT,group = STUDYf),outlier.shape = NA)
  plotobj2 <- plotobj2 + scale_x_discrete("\nStudy")
  plotobj2 <- plotobj2 + scale_y_continuous("Time under target trough (days)\n")
  print(plotobj2)
```

## Proportion of individuals below target at time = 546 days

```{r,echo = TRUE,warning = FALSE}
# Use subsetted data for only time == 546 (all.data.546)
  all.data.546$BTT <- 0
  all.data.546$BTT[all.data.546$IPRE < trough.target] <- 1  # Below trough target (BTT) == 1 for IPRE < 3
  summary.BTT.546 <- ddply(all.data.546, .(STUDYf), function(all.data.546) sum(all.data.546$BTT))
# Add further information to summary.BTT.546
  names(summary.BTT.546)[2] <- "nBTT"  # Number of individuals below trough target
  summary.BTT.546$n <- n*nsim # Number of individuals in the study population
  summary.BTT.546$pBTT <- round(summary.BTT.546$nBTT/summary.BTT.546$n,digits = 3)  # Proportion of individuals BTT
  print(summary.BTT.546)
```

## Which individuals are below the target at time = 546 days?

```{r,echo = TRUE,warning = FALSE}
# Subset all.data.546 for BTT == 1
  all.data.546.BTT <- all.data.546[all.data.546$BTT == 1,]
  summary.BTT.546.ID <- ddply(all.data.546.BTT, .(ID,STUDYf), function(all.data.546.BTT) sum(all.data.546.BTT$BTT))
  # Add some descriptions to seeds (ID)
    # Final albumin
      summary.BTT.546.ID$FINAL_ALB <- "3 U/L"
      summary.BTT.546.ID$FINAL_ALB[summary.BTT.546.ID$ID %in% c(2,4,8,11)] <- "4 U/L"
      summary.BTT.546.ID$FINAL_ALB[summary.BTT.546.ID$ID %in% c(3,6,9,12)] <- "5 U/L"
    # Onset of ADA
      summary.BTT.546.ID$ADA_ONSET <- "Never"
      summary.BTT.546.ID$ADA_ONSET[summary.BTT.546.ID$ID %in% c(1,2,3)] <- "154 days"
      summary.BTT.546.ID$ADA_ONSET[summary.BTT.546.ID$ID %in% c(4,5,6)] <- "294 days"
      summary.BTT.546.ID$ADA_ONSET[summary.BTT.546.ID$ID %in% c(7,8,9)] <- "462 days"
  # Make an IDf column
    summary.BTT.546.ID$IDf <- paste0(summary.BTT.546.ID$FINAL_ALB," ",summary.BTT.546.ID$ADA_ONSET)  

# Plot 
  plotobj3 <- NULL
  plotobj3 <- ggplot(summary.BTT.546.ID)
  plotobj3 <- plotobj3 + geom_point(aes(x = FINAL_ALB,y = V1,colour = ADA_ONSET),size = 4,alpha = 0.3)
  plotobj3 <- plotobj3 + geom_point(aes(x = FINAL_ALB,y = V1,colour = ADA_ONSET),size = 4,shape = 1)  
  plotobj3 <- plotobj3 + scale_x_discrete("\nSeed's Final Albumin")
  plotobj3 <- plotobj3 + scale_y_continuous("Number below target trough (time = 546)\n")
  plotobj3 <- plotobj3 + facet_wrap(~STUDYf,ncol = 5)
  print(plotobj3)
```

## Summary of findings

1.  Label-recommended dosing (5 mg/kg) is the regimen least likely to maintain trough concentrations above the target (3 mg/L)
2.  Clinical dosing (adjusting doses on isolated, sampled concentrations) performs well compared to the Bayesian-guided dosing studies - in terms of time spent under the target trough concentration and number individuals below the target trough concentration at day 546
3.  Of the Bayesian-guided dosing studies, time-weighting with a Q of 1.01 appears to have the lowest median time spent under the target trough and individuals below the target trough concentration at day 546
    + However, I would argue that this is not signficantly different from Q = 1.005 or clinical dosing
4.  Individuals who have onset of ADA in the last interval (i.e., at 462 days) are more likely to be below the target trough by day 546.  This is likely because the last dose was optimised/adjusted at day 378 and would not have accounted for the onset of ADA occurring in the next interval
5.  Individuals with albumin progressing to 3 U/L by the end of the study are more likely to be under the target trough concentration by day 546 - low albumin increases infliximab's clearance.  After day 378 (last dose adjustment), albumin continues to decline for these individuals and is not accounted for when making dosing predictions
6.  No dose-adjustment regimen here appears to be superior at maintaining trough concentrations above the target.  In all studies, there is wide variability in concentrations throughout the study-period despite somewhat individualised dose adjustments.  Perhaps a new method needs to be proposed?

### Ideas

* Only 200 simulations per seed were performed.  I have data for 100 simulations and can try and see if there is a difference.  If there is a difference between 100 and 200 simulations, then I'll go for 500 simulations
    + May need a large number of simulations owing to the time-dependent random effects in this population
* Propose a time-weighting system that is based on the drug's half-life - i.e., gives much less-weighting for older samples when half-life for the individual is short, and gives equal weighting to older samples when the half-life for the individual is long
* When making dosing predictions, always assume that onset of ADA may occur in the next interval
* Optimise dosing from the beginning of the first interval (i.e., first dose) based on baseline albumin - rather than waiting 3 doses and more than 3 months to optimise the dose